A secondary screen architecture to accurately capture viewers' interactions in an iTV environment

### 2014-06-02 src/paper.tex
WIP: Editing the introduction

\begin{abstract}
TV watching is frequently seen as a social activity. People gather around the television for entertainment or information. Advances in TV technology have enabled the viewer to actively interact with the TV through interactive applications instead of just passively watching TV. Since the TV set is shared by many people and the interaction occurs by using a single remote control, it is difficult to accurately capture the individual needs from each viewer. It is also difficult to identify the context in which the interactions occur, e.g., to manage uniquely who is present in the environment and what is being watched on TV. In this paper, we present a novel architecture that facilitates viewers' individual interactions and contextual information in shared TV environments. One important application for this data consists of generating personalized content for single viewers and groups of viewers.
\end{abstract}

@@

TV watching is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information. After many advances in technologies, for interactive and digital TV, it is possible to develop high-level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume. As a result, considering the interactions of millions of viewers, the captured data can provide valuable information for content providers (CPs)~\cite{Teixeira2010}.

The conventional remote control(RC) is typically used as a standard medium for viewers to interact with their TVs. However, the interaction by using the RC presents two notable problems: (1) to automatically identify the viewers who have possession of it; and (2) to capture viewers' interactions and the context in which they occur. As a consequence, the entire group of viewers (e.g., a family) is treated as a single viewer. As a result, the tastes that were inferred from the users in charge of the RC can be imposed on the tastes of the others.

For example, the CPs can obtain the user ratings given to TV programs, amount of viewers, and user profiles. By using proper machine learning algorithms, CPs can infer viewers' tastes from audience data in order to deliver personalized content~\cite{Kim2012,Shin2009}. However, identifying viewers and capturing their individual interactions are still a challenging activity in the traditional TV environment.

The conventional RC presents two notable problems for capturing interactions from viewers: (1) to automatically identify the viewers that are in the TV environment in order to contextualize the interaction; and (2) to individually capture interactions from the viewer in charge of the RC. Thus, considering a scenario with the traditional TV environment and a conventional TV, all interactions are assigned to the whole group of viewers (e.g., a family), rather than to the viewer in charge of the RC. As a result, the tastes that were inferred from the users in charge of the RC can be imposed on the tastes of the others.

As a potential alternative to handle the limitations of the RC, the proliferation of personal mobile devices has changed the people behavior towards audiovisual content consumption in interactive TV environments. Nowadays, viewers rarely just sit passively and watch TV. In many situations, they use their personal devices as a secondary screen to perform activities related to TV watching, which end up enriching and immersing the user into the TV experience.

Secondary screen devices arise as a powerful mechanism to accurately identify viewers and  capture their interactions. In this research field, a typical approach is to use personal devices (e.g., smartphones and tablets) as secondary screens~\cite{Courtois2012}, since they are almost ubiquitous and present good graphical capabilities. The connectivity capabilities of smartphones were used in~\cite{Cabarcos2011}, where the Bluetooth technology was used to detect nearby users. With respect to interaction capture, an approach described in~\cite{Teixeira2010} has shown an architecture to capture contextualized viewers interactions through a conventional RC. In this paper, we present a novel architecture that facilitates the identification of viewers, which is useful to contextualize the interactions. In addition, the identification of viewers facilitates the capture of their individual interactions.

@@

\section{Architecture}

@@

>>>>

\begin{abstract}
TV watching is frequently seen as a social activity. People gather around the television for entertainment or information. Advances in TV technology have enabled the viewer to actively interact with the TV through interactive applications instead of just passively watching TV. Since the TV set is shared by many people and the interaction occurs by using a single remote control, it is difficult to accurately capture the individual needs from each viewer. It is also difficult to identify the context in which the interactions occur, e.g., to manage uniquely who is present in the environment and what is being watched on TV. In this paper, it is presented a novel architecture that facilitates viewers' individual interactions and contextual information in shared TV environments. One important application for this data consists of generating personalized content for single viewers and groups of viewers.
\end{abstract}

@@

TV watching is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information. After many advances in technologies, for interactive and digital TV, it is possible to develop high-level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume. Considering the interactions of millions of viewers, the generated data can provide valuable information for content providers (CPs)~\cite{Teixeira2010}.

The conventional remote control (RC) is typically used as a standard medium for viewers to interact with their TVs. However, this medium presents two notable problems: (1) to automatically identify the viewers who have possession of the RC; and (2) to capture contextualized viewers' interactions. As a result, the entire group of viewers (e.g., a family) is treated as a single viewer and the tastes that were inferred from the users in charge of the RC can be imposed on the tastes of the others.

Given the limitations of the conventional RC, a novel secondary screen architecture to identify viewers who are interacting with interactive TV (iTV) services is presented in this paper. Personal devices (e.g., smartphones and tablets) are used as secondary screens with the aim of capturing personal and contextualized interactions for each individual viewer in the iTV environment. By using proper machine learning algorithms, CPs can infer viewers' tastes from audience data in order to deliver personalized content~\cite{Kim2012,Shin2009}.

% The approach described in this paper is based on the development of web services that provide means to access content from the CP and

% Since, each viewer has its own personal device as secondary screen

% A range of Applications and iTV services can be developed to obtain the user ratings given to TV programs, amount of viewers, and user profiles. .

Data about viewers' interactions are captured by personal devices (e.g., smartphones and tablets) that are used to mediate the interaction between viewers and the iTV device.

Personal devices (e.g., smartphones and tablets) are almost ubiquitous and present rich interactive capabilities.

As a potential alternative to handle the limitations of the RC, the proliferation of personal mobile devices has changed the people behavior towards audiovisual content consumption in interactive TV environments.

Secondary screen devices arise as a powerful mechanism to accurately identify viewers and  capture their interactions. In this research field, a typical approach is to use personal devices (e.g., smartphones and tablets) as secondary screens~\cite{Courtois2012}, since they are almost ubiquitous and present good graphical capabilities. The connectivity capabilities of smartphones were used in~\cite{Cabarcos2011}, where the Bluetooth technology was used to detect nearby users. With respect to interaction capture, an approach described in~\cite{Teixeira2010} has shown an architecture to capture contextualized viewers interactions through a conventional RC.

@@

\section{Secondary Screen Architecture and Implementation}

@@

Nowadays, viewers rarely just sit passively and watch TV. In many situations, they use their personal devices as a secondary screen to perform activities related to TV watching, which end up enriching and immersing the user into the TV experience.
